Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 method.tex
Minor corrections in section 2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1031 ccdd05d5-56c1-461a-bf98-85f6876523b4

Equation~(\ref{eq:SNRTD}) can be implemented in the time-domain as an
finite impulse response (\fir) filter, requiring $\mathcal O(\numtmps
\tmpsamps)$ floating point operations per sample.  However, it is typically
much more computationally efficient to use the convolution theorem and the
\fft\ to implement fast convolution in the frequency-domain, requiring only
$\mathcal O(\numtmps \lg \tmpsamps)$ operations per sample with increased
latency.

>>>>

Equation~(\ref{eq:SNRTD}) can be implemented in the time-domain as bank of
finite impulse response (\fir) filter, requiring $\mathcal O(\numtmps
\tmpsamps)$ floating point operations per sample.  However, it is typically
much more computationally efficient to use the convolution theorem and the
\fft\ to implement fast convolution in the frequency domain, requiring only
$\mathcal O(\numtmps \lg \tmpsamps)$ operations per sample but incurring
a latency comparable to the length of the templates.
